UGAN: Improving Underwater Image Quality using Generative Adversarial Networks

### 2017-09-16 files/paper/tex/methodology.tex
update

\section{Methodology}
\label{sec:methodology}
\starnote{A short summary of the method needs to go here, like an overview, so the reader can `stay in the loop' so to speak.}

>>>>

\section{Methodology}
\label{sec:methodology}
Underwater images distorted by color or circumstance lack ground truth, which is a necessity for previous colorization
approaches. Furthermore, the distortion present in an underwater image is highly nonlinear; simple methods such as
adding a hue to an image do not capture all of the dependencies. We propose to use CycleGAN as a distortion model in
order to generate paired images for training. Given a domain of underwater images with no distortion, and a domain of
underwater images with distortion, CycleGAN is able to perform style transfer. Given an undistorted image, CycleGAN
distorts it such that it appears to have come from the domain of distorted images. These pairs are then used in our
algorithm for image reconstruction.
